SHORT: Longitudinal Study of Software Environments Produced by Dockerfiles from Research Artifacts: Initial Design

### 2025-06-09 src/main.tex
with the 1-page rebuttal
de-anonymise

\title{%
  % (Very) Preliminary Study of the Longevity of Docker Images from Research Artifacts
  SHORT: Longitudinal Study of Software Environments Produced by Dockerfiles from Research Artifacts: Initial Design% and Results
}

@@

% \author{Quentin Guilloteau}
% \orcid{0009-0003-7645-5044}
% \email{Quentin.Guilloteau@inria.fr}
% \affiliation{%
%   \institution{Inria, CNRS, ENSL, UCBL1, LIP}
%   \city{Lyon}
%   \country{France}
% }
% 
% \author{Antoine Waehren}
% \email{A.Waehren@stud.unibas.ch}
% \affiliation{%
%   \institution{University of Basel}
%   \city{Basel}
%   \country{Switzerland}
% }
% 
% \author{Florina M. Ciorba}
% \email{Florina.Ciorba@unibas.ch}
% \affiliation{%
%   \institution{University of Basel}
%   \city{Basel}
%   \country{Switzerland}
% }

\author{Anonymous Authors}
\email{Anonymous email}
\affiliation{%
  \institution{Anonymous Institution}
  \city{Anonymous City}
  \country{Anonymous Country}
}

@@

We wrote the descriptions in Nickel (see Section~\ref{sec:nickel}) for the five artifacts of the Euro-Par 2024 conference that used a Docker container to share their software environments, and used \ecg\ to build their associated \df s once every month for seven months.
% "2024-10-01" "2024-11-04" "2024-12-02" "2025-01-02" "2025-02-05" "2025-03-12" "2025-04-01"
The initial build was October 1$^{st}$ 2024, then the following builds were on November 4$^{th}$ 2024, December 2$^{nd}$ 2024, January 2$^{nd}$ 2025, February 5$^{th}$ 2025, March 12$^{th}$ 2025, and April 1$^{st}$ 2025.
The deadline for the authors to submit their artifacts to Euro-Par 2024 was May 15$^{th}$ 2024\footnote{\url{https://2024.euro-par.org/calls/artifacts/}}.
Hence, our initial build took place almost 5 months after the artifacts submission.
The following sections follow the dimensions captured by \ecg\ (see Section~\ref{sec:ecg:capture}).
The data collected and presented in this section is available on Zenodo~\cite{dataset_europar24}.

>>>>

\title{%
  SHORT: Longitudinal Study of Software Environments Produced by Dockerfiles from Research Artifacts: Initial Design% and Results
}

@@

\author{Quentin Guilloteau}
\orcid{0009-0003-7645-5044}
\email{Quentin.Guilloteau@inria.fr}
\affiliation{%
  \institution{Inria, CNRS, ENSL, UCBL1, LIP}
  \city{Lyon}
  \country{France}
}

\author{Antoine Waehren}
\orcid{0009-0003-9852-8865}
\email{A.Waehren@stud.unibas.ch}
\affiliation{%
  \institution{University of Basel}
  \city{Basel}
  \country{Switzerland}
}

\author{Florina M. Ciorba}
\orcid{0000-0002-2773-4499}
\email{Florina.Ciorba@unibas.ch}
\affiliation{%
  \institution{University of Basel}
  \city{Basel}
  \country{Switzerland}
}

% \author{Anonymous Authors}
% \email{Anonymous email}
% \affiliation{%
%   \institution{Anonymous Institution}
%   \city{Anonymous City}
%   \country{Anonymous Country}
% }

@@

We wrote the descriptions in Nickel (see Section~\ref{sec:nickel}) for the five artifacts of the Euro-Par 2024 conference that used a Docker container to share their software environments, and used \ecg\ to build their associated \df s once every month for seven months.
% "2024-10-01" "2024-11-04" "2024-12-02" "2025-01-02" "2025-02-05" "2025-03-12" "2025-04-01"
The initial build was October 1$^{st}$ 2024, then the following builds were on November 4$^{th}$ 2024, December 2$^{nd}$ 2024, January 2$^{nd}$ 2025, February 5$^{th}$ 2025, March 12$^{th}$ 2025, and April 1$^{st}$ 2025.
The deadline for the authors to submit their artifacts to Euro-Par 2024 was May 15$^{th}$ 2024.
%\footnote{\url{https://2024.euro-par.org/calls/artifacts/}}.
Hence, our initial build took place almost 5 months after the artifacts submission.
The following sections follow the dimensions captured by \ecg\ (see Section~\ref{sec:ecg:capture}).
The data collected and presented in this section is available on Zenodo~\cite{dataset_europar24}.
